TBD

### 2016-10-19 paper.tex
LOGCAL sort of complete
reformatting the start of the paper

 \section{Visibilities}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ can be described as

@@

\subsection{Redundant Array Geometry Function}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

@@

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_red_vec}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

With the aid of Eq.~\eqref{eq:logcal_amp} we can construct the following linear system:
\begin{equation}
\label{eq:log_system}
\bdelta = \bJ\bzeta + \bs, 
\end{equation}
where
\begin{align}
\left [ \bdelta \right ]_{\alpha_{pq}} &= \ln |d_{pq}|, & \left [ \bs \right ]_{\alpha_{pq}} = s_{pq} 
\end{align}
and
\begin{equation}
\left [ \bzeta \right ]_{\alpha_{pq}} = \begin{cases} \ln |g_j| & \textrm{if}~i\leq N \\ \ln |y_{j-N}| & \textrm{otherwise} \end{cases}. 
\end{equation}
Furthermore,
\begin{equation}
\bJ = 
\begin{bmatrix}
\bN & \bM
\end{bmatrix}
\end{equation}
with 
\begin{equation}
[\bN]_{\alpha_{pq},j} = \begin{cases}
       1 & \textrm{if}~(p=j)~\textrm{or}~(q=j)\\
       0 & \textrm{otherwise}
      \end{cases}
\end{equation}
and
\begin{equation}
[\bM]_{\alpha_{pq},j} = \begin{cases}
       1 & \textrm{if}~\phi_{pq}=j\\
       0 & \textrm{otherwise}
      \end{cases}
\end{equation}

>>>>

\section{Preliminaries}

\subsection{Measurement Equation}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ can be described as

@@

\subsection{Indexing Functions}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

@@

\subsection{Redundant Measurement Equation}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g_q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_red_vec}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

With the aid of Eq.~\eqref{eq:logcal_amp} we can construct the following linear system:
\begin{equation}
\label{eq:log_system}
\bdelta = \bJ\bzeta + \bs, 
\end{equation}
where
\begin{align}
\left [ \bdelta \right ]_{\alpha_{pq}} &= \ln |d_{pq}|, & \left [ \bs \right ]_{\alpha_{pq}} = s_{pq} 
\end{align}
and
\begin{equation}
\left [ \bzeta \right ]_{j} = \begin{cases} \ln |g_j| & \textrm{if}~j\leq N \\ \ln |y_{j-N}| & \textrm{otherwise} \end{cases}. 
\end{equation}
Furthermore,
\begin{equation}
\bJ = 
\begin{bmatrix}
\bN & \bM
\end{bmatrix}
\end{equation}
with 
\begin{equation}
[\bN]_{\alpha_{pq},j} = \begin{cases}
       1 & \textrm{if}~(p=j)~\textrm{or}~(q=j)\\
       0 & \textrm{otherwise}
      \end{cases}
\end{equation}
and
\begin{equation}
[\bM]_{\alpha_{pq},j} = \begin{cases}
       1 & \textrm{if}~\phi_{pq}=j\\
       0 & \textrm{otherwise}
      \end{cases}
\end{equation}
